 


\section{Problem 1}
\label{part1}
\begin{enumerate}
\item Write a Python program that extracts 1000 unique links from
Twitter.  You might want to take a look at:

http://thomassileo.com/blog/2013/01/25/using-twitter-rest-api-v1-dot-1-with-python/

\item But there are many other similar resources available on the web.  Note
that only Twitter API 1.1 is currently available; version 1 code will
no longer work.

\item Also note that you need to verify that the final target URI (i.e., the
one that responds with a 200) is unique.  You could have different
shortened URIs for www.cnn.com.  For example, 

http://cnn.it/1cTNZ3V\\
http://t.co/BiYdsGotTd

\item Both ultimately redirect to cnn.com, so they count as only 1 unique URI.
Also note the second URI redirects twice -- don't stop at the first
redirect.

You might want to use the search feature to find URIs, or you can
pull them from the feed of someone famous (e.g., Tim O'Reilly).

Hold on to this collection -- we'll use it later throughout the semester.
\end{enumerate}

\subsection{Solution}

Extracting 1000 unique links from Twitter was more complex endeavor than expected. 

The following steps were taken in order to get the links 
\begin{enumerate}
\item First the key and secret keys for OATH and API are collected by registering an Application in Twitter with an account.
\item TwitterSearch package is used to get the URI's from tweets for a specific keyword.
\item All the URI's that are present in the tweets got from the search for a particular key word are put in an array set. By keeping it in a set eliminates the redundant entries. 
\item Then checked whether the Url's are redirected to same website or not and also checked whether the extracted url is working or not. 
\item To get the URLs form tweets it take so long and apart from that i faced the 429 error which says "too many requests", so i will have to waiti for 15 minutes to run the next time. 
\item When I searched for 5000 urls form the tweets I got only 480 unique links out of them. so I kept incrasing the count to get 1000 unique links
\item When I increased the count to 17000 I got 1500 unique links and this script took almost 40 minutes to run. 
\item I could not even split the program into two different script as there might be repetition in the output got from both the scripts so I will have to run it in a single script.    
\item This way collected 1000 URI's for keyword "twitter". 
\end{enumerate}
\newpage
\subsection{Code Listing}
Here is the python code that is used to collect Thousand URL's from twitter. 


\lstinputlisting[language=Python,breaklines = true,frame=single,caption={Python program for acquiring 1000 unique links for a given keyword}, label=lst:q1-1,captionpos=b,numbers=left,showspaces=false,showstringspaces=false,basicstyle=\footnotesize]{list_unique_links.py}
\newpage
\subsection{Results}


\verbatiminput{samplelinks.txt}

